A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-06 manuscript.Rmd
remove gert, its not needed for the tutorial

A significant hurdle for adopting the before-mentioned tools for researchers is that they are typically used through a command-line interface (CLI).
The CLI predates and coexists with graphical user interfaces (GUIs) which many users (including the authors) prefer over the text-based interactions of a CLI for most tasks.
A GUI has the apparent disadvantages for reproducibility that it requires a user who clicks on the correct buttons in the correct order.
Depending on the number of steps, this is not only much effort but also error-prone.
This tutorial seeks a compromise.
We use simpler alternatives, including a GUI where we can, to create a reproducible workflow, but the reproduction of such workflow does not rely on manual steps.
At several points, we rely on or have self-developed a CLI that wraps a more complicated (and powerful) CLI.
These wrappers use standard CLI tools but provide feedback for the user about what the computer does and what the user should do in layman's terms and are accessible from within R.
We hope this makes reproducibility tools more accessible by enabling untrained users to detect their systems state accurately and act correspondingly [@parasuramanAutomationHumanPerformance2018, Chapter 8: "Automation and Situation Awareness"].
These alternative tools are merely an assistance system, and as users get more and more comfortable, they can use the underlying tools directly to solve more complex problems.
Please install the package [`gert`](https://github.com/r-lib/gert)[@R-gert] which wraps Git commands and [`repro`](https://github.com/aaronpeikert)[@R-repro] so they can act as assistance systems while you follow the tutorial:

```{r, eval=FALSE}
install.packages("gert")
# repro is not on CRAN yet
install.packages('repro', repos = 'https://aaronpeikert.r-universe.dev')
```

@@

However, users do not have to have repro installed, in fact, they do not even need R installed. 
The two Make commands `make docker` and `make -B DOCKER=TRUE` together with an installation of Make and Docker are sufficient.
They can be pasted into a terminal and will reproduce the project in many cases.

>>>>

A significant hurdle for adopting the before-mentioned tools for researchers is that they are typically used through a command-line interface (CLI).
The CLI predates and coexists with graphical user interfaces (GUIs) which many users (including the authors) prefer over the text-based interactions of a CLI for most tasks.
A GUI has the apparent disadvantages for reproducibility that it requires a user who clicks on the correct buttons in the correct order.
Depending on the number of steps, this is not only much effort but also error-prone.
This tutorial seeks a compromise.
We use simpler alternatives, including a GUI where we can, to create a reproducible workflow, but the reproduction of such workflow does not rely on manual steps.
At several points, we rely on or have self-developed a CLI that wraps a more complicated (and powerful) CLI.
These wrappers use standard CLI tools but provide feedback for the user about what the computer does and what the user should do in layman's terms and are accessible from within R.
We hope this makes reproducibility tools more accessible by enabling untrained users to detect their systems state accurately and act correspondingly [@parasuramanAutomationHumanPerformance2018, Chapter 8: "Automation and Situation Awareness"].
These alternative tools are merely an assistance system, and as users get more and more comfortable, they can use the underlying tools directly to solve more complex problems.
Please install the package [`repro`](https://github.com/aaronpeikert)[@R-repro] so it can act as assistance systems while you follow the tutorial:

```{r, eval=FALSE}
# repro is not on CRAN yet
install.packages('repro', repos = 'https://aaronpeikert.r-universe.dev')
```

@@

However, users do not have to have repro installed to reproduce a project, in fact, they do not even need R installed. 
The two Make commands `make docker` and `make -B DOCKER=TRUE` together with an installation of Make and Docker are sufficient.
They can be pasted into a terminal and will reproduce the project in many cases.
